How to use replication assignments for teaching integrity in empirical archaeology

### 2019-08-17 README.Rmd
update readme to show supplementary materials

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations

>>>>

- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)    
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations
- [:file_folder: supplementary-materials](/analysis/supplementary-materials): Supplementary materials including the assignment instructions that we used with the students, and two completed assignments submitted by students in this class.
